### 2017-03-11 thesis/results/results.tex
Really finished the draft for appendix A - tmp commit

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cris_crdeg_trans_meta}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cris_cr_trans_meta}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cris_cr_trans_meta}
	\caption[Cr obesity associated metagene in \gls{nzbc} data]{Heatmap, box plot and scatter plot showing the association of Cr obesity associated metagene with sample gene expression, \gls{bmi} and \gls{bmi} status from \gls{nzbc} data, respectively.
	The results for other metagenes are in \cref{app:a}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:degmetaprint}
\end{figure}

>>>>

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cris_crdeg_trans_meta}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cris_crdeg_trans_meta}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cris_crdeg_trans_meta}
	\caption[Cr obesity associated metagene in \gls{nzbc} data]{Heatmap, box plot and scatter plot showing the association of Cr obesity associated metagene with sample gene expression, \gls{bmi} and \gls{bmi} status from \gls{nzbc} data, respectively.
	The results for other metagenes are in \cref{app:a}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:degmetaprint}
\end{figure}
